Air cargo load and route planning in pickup and delivery operations

### 2023-06-09 CAIE/cie.tex
Experimentations ended
New experimentation to cie.tex
Alternative to table 9

\begin{table}[H]
	\centering
	\caption{Solutions with different time limitations for $S_K$ tours.}  \label{tab:100time}
	\footnotesize
	\begin{tabular}{ccc|cc|cc|cc}
		\toprule
		&             \multicolumn{2}{r}{\bf Volume $surplus$} &\multicolumn{2}{c}{$1.2$}&\multicolumn{2}{c}{$1.5$}&\multicolumn{2}{c}{$2.0$} \\
		\midrule
		$method$& {\bf \specialcell{Time\\limit (s)}} & {\bf Scenarios}    & {\bf 4} & {\bf 5} & {\bf 4} & {\bf 5} & {\bf 4} & {\bf 5} \\
		\toprule

		\multirow{6}{*}{\it Gurobi* }& \multirow{2}{*}{1200} & $f$ & 14.67   & x       &  20.64  &  x      & 27.97   & x \\ % 
		&        &  {\bf run time (s)}                             & 217     & x       &  304    &  x      & 579     & x \\ % 
		\cmidrule(lr){2-9}                              
		& \multirow{2}{*}{2400}& $f$                               & 14.59   &         &  20.60  &  x      & 29.10   & x \\ % 
		&        &  {\bf run time (s)}                             & 313     &         &  327    &  x      & 543     & x \\ % 
		\cmidrule(lr){2-9}                              		
		& \multirow{2}{*}{3600}& $f$                               & 14.61   & x       &  20.59  & 18.36   & 29.11   & x \\ % 
		&        &  {\bf run time (s)}                             & 297     & x       &  470    & 2241    & 689     & x \\ % 		
		\midrule
		\multirow{6}{*}{\it Shims}   & \multirow{2}{*}{1200} & $f$ & 14.53   & 13.42   &  20.45  & 18.00   & 28.98   & 26.08 \\ % 
		&        & {\bf run time (s)}                              & 18      & 109     &  26     & 160     & 37      & 203   \\ % 
		\cmidrule(lr){2-9}                              
		& \multirow{2}{*}{2400}& $f$                               & 14.53   & 13.42   &  20.45  & 18.00   & 28.98   & 26.08 \\ % 
		&        &  {\bf run time (s)}                             & 18      & 107     &  25     & 159     & 37      & 192   \\ % 	
		\cmidrule(lr){2-9}                              
		& \multirow{2}{*}{3600} & $f$                              & 14.53   & 13.42   &  20.45  & 18.00   & 28.98   & 26.08 \\ %  
		&        &  {\bf run time (s)}                             & 17      & 106     &  26     & 157     & 37      & 181   \\ %  
		\bottomrule

		&                                       & {\bf Normalized} & 0.99    & x       & 0.99    & 0.98    & 1.00    & x\\
		&                                       & {\bf Speed-up}   & 15.6    & x       & 14.3    & 14.3    & 16.3    & x\\

@@

>>>>

\begin{table}[H]
	\centering
	\caption{Solutions with different time limitations for $S_K$ tours.}  \label{tab:100time_2}
	\footnotesize
	\begin{tabular}{ccc|ccc|ccc|ccc}
		\toprule
		&             \multicolumn{2}{r}{\bf Volume $surplus$} &\multicolumn{3}{c}{$1.2$}&\multicolumn{3}{c}{$1.5$}&\multicolumn{3}{c}{$2.0$} \\
		\midrule
		$method$& {\bf limit (s)} & {\bf Scenarios}&{\bf 3}&{\bf 4}&{\bf 5}&{\bf 3}&{\bf 4}&{\bf 5}&{\bf 3}&{\bf 4}&{\bf 5} \\
		\toprule

		\multirow{8}{*}{\it Gurobi } & \multirow{2}{*}{240*} & $f$ & 13.34 &  x      &  x      & 18.31 &  x      &  x      & x     & x       & x \\ % 
&               &  {\bf run time (s)}                              & 123   &  x      &  x      & 181   &  x      &  x      & x     & x       & x \\ % 
\cmidrule(lr){2-12}

		&                              \multirow{2}{*}{1200} & $f$ & 13.31 & 14.67   & x       & 18.25 &  20.64  &  x      & 26.49 & 27.97   & x \\ % 
		&        &  {\bf run time (s)}                             & 129   & 217     & x       & 190   &  304    &  x      & 384   & 579     & x \\ % 
		\cmidrule(lr){2-12}                              
		& \multirow{2}{*}{2400}& $f$                               & 13.30 & 14.59   & 13.59   & 18.25 &  20.60  &  x      & 26.46 & 29.10   & x \\ % 
		&        &  {\bf run time (s)}                             & 127   & 313     & 1444    & 188   &  327    &  x      & 381   & 543     & x \\ % 
		\cmidrule(lr){2-12}

		& \multirow{2}{*}{3600}& $f$                               & 13.32 & 14.61   & x       & 18.25 &  20.59  & 18.36   & 26.46 & 29.11   & x \\ % 
		&        &  {\bf run time (s)}                             & 121   & 297     & x       & 193   &  470    & 2241    & 319   & 689     & x \\ %

		 \multirow{2}{*}{\it Shims} & \multirow{2}{*}{240*}  & $f$ & 13.23 & 14.53   & 13.42   & 18.21 &  20.45  & 18.00   & 26.38 & 28.98   & 26.08 \\ % 
		&         & {\bf run time (s)}                             & 6     & 17      & 109     & 8     &  26     & 160     & 13    & 37      & 229   \\ %

@@

		&                                       & {\bf Normalized} & 0.99  & 0.99    & 0.99    & 1.00  & 0.99    & 0.98    & 1.00  & 1.00    & x\\
		&                                       & {\bf Speed-up}   & 20.9  & 15.6    & 13.5    & 23.8  & 14.3    & 14.3    & 29.0  & 16.3    & x\\

		\bottomrule
				\multicolumn{12}{c}{*4 minutes is the time {\it Shims} needs to solve a seven-node tour.}\\
	\end{tabular}
	\normalsize
\end{table}

According to the results in Table \ref{tab:100time}, {\it Shims} was 15 times faster than {\it Gurobi* } to solve the ACLP-RPDP, and {\it Gurobi* } was not fully capable of solving scenario 5.
